---
title: "R Exercises"
author: "Gabriel Crone"
date: "`r Sys.Date()`"
output: pdf_document
---

This document compiles my solutions from the R exercises from a book by Grinberg & Reed's "Programming Exercises for R."

# Part 1: Vectors
## 1.
```{r 1.1, name = "my_chunk"}
# a)
1:20

# b)
20:1

# c)
c(1:20, 19:1) # OR c(1:19, 20:1)

# d)
tmp <- c(4, 6, 3)

# e)
rep(tmp, 10)

# f)
c(rep(tmp, 10), 4)

# g)
c(
  rep(4,10),
  rep(6, 20),
  rep(3, 30)
)
```

## 2.
```{r 1.2}
seq <- seq(3, 6, 0.1)
exp(seq) * cos(seq)

```

## 3.
```{r 1.3}
# a)
exp1 <- seq(3,36,3)
exp2 <- seq(1, 34, 3)
(0.1^exp1)*(0.2^exp2)

# b)
num <- 2^(1:25)
denom <- 1:25
num/denom
```

## 4.
Note that `i` as a name for index cannot be used, since it's already an identified object in R.

```{r 1.4}
# a)
index <- 10:100
sum(index^3 + 4*index^2)

# OR as for loop
vec <- c()
for(i in 10:100) {
  vec[i - 9] <- i^3 + 4*i^2
}
sum(vec)

# b) 
index <- 1:25
sum(
  ((2^index)/index) + (3^index)/(index^2)
)

# OR with for loop
vec <- c()
for(i in 1:25) {
  vec[i] <- ((2^i)/i) + ((3^i)/(i^2))
}
sum(vec)
```

## 5.
```{r 1.5}
# a)
paste("label", 1:30)

# b)
paste0("fn", 1:30)
```

## 6.
```{r 1.6}
# Setup
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T)

# a)
yVec[-1]-xVec[-length(xVec)]

# b)
sin(yVec[-length(yVec)])/cos(xVec[-1])

# c)
# Shortcut to using base R is using head and 
# -number, where number is number of values
# to "snip" off from the end.
head(xVec, -2) + 2*head(xVec, -1)[-1] + -1*xVec[-(1:2)]


# d)
exp(-xVec[-1]) / (head(xVec, -1) + 10)

```

## 7.
Tip 1: `which({condition})` returns the position values of the vector for which the condition specified is TRUE. With those values, need to index them in with `[]`.

Tip 2: The `order()` function returns the indices of an ordered vector, allowing you to use indices in rearranging of other vector (e.g., in part g).


```{r 1.7}
# a)
yVec[which(yVec > 600)]

# b)
which(yVec > 600)

# c)
xVec[which(yVec > 600)]

# d)
sqrt(abs(xVec - mean(xVec)))

# Now is a good place to use pipes
# (makes it more readable)
(xVec - mean(xVec)) |>
  abs() |>
  sqrt()

# e)
sum(
  # Returns TRUE if condition met per element
  # and FALSE otherwise.
  yVec <= max(yVec) & 
  yVec > max(yVec)-200
)

# f)
sum(xVec %% 2)

# g)
xVec[order(yVec)]

# h)
yVec[seq(1, length(yVec), 3)]
```

## 8.
It's important to recognize that a) the numerators of each are all even numbers (and 1) up to 38, and b) the denominators are all odd numbers up to 39.

```{r 1.8}
num <- c(1, seq(2, 38, 2))
denom <- seq(1, 39, 2)
cumprod(num/denom)
```

# Part 2: Matrices



